\documentclass{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}  

\begin{document}

\part{Pedro Vanzella}

\personal
    [pedrovanzella.com]
    {Toronto, ON}
    {}
    {pedro@pedrovanzella.com}

    \section{Experience}

    \begin{eventlist}

    \item{May 2017 - Present}
      {Rails, AWS, Sidekiq}
      {Toptal - Tatango}

      Work on the backend of a high availability and high throughput SMS
      marketing application. Developed A/B Testing features and updated a
      100+ model legacy application.

    \item{July 2016 - April 2017}
      {Rails, React}
      {Toptal - Aflutter}

      Maintanance and development of a wedding planning application in Rails and
      React.

    \item{May 2016 - July 2016}
      {Django}
      {Toptal - SpokeHub}

      Maintanance and development of an ERP in Django.

    \item{November 2015 - April 2016}
      {Rails API}
      {Toptal - BuildRX}

      Development of microservices for e-Commerce in Rails, using only the API features.

    \item{May 2015 - November 2015}
      {Python, C, JavaScript, AngularJS}
      {CWI Software - Renner}
      
      Development of an interactive kiosk. A Python middleware bridges the hardware, a
      Java back-end and C libraries to a Webkit browser. The browser calls the Python
      classes and exports them to JavaScript, where they are called by an AngularJS front-end.

    \item{January 2015 - May 2015}
      {Python, Flask, MongoDB}
      {CWI Software - Terra}

      Maintanance and development of a Video On Demand system for a large ISP and
      content provider. Written in Flask with MongoDB.

    \item{Januray 2014 - December 2014}
      {Ruby, Rails, MongoDB}
      {Fator7 - StarlightLED}

      Development of a Cloud control system for a class of Internet of Things devices,
      including public lights and traffic controllers.

    \item{August 2013 - December 2013}
      {Ruby, Rails, Postgres}
      {Toptal - USEED}

      Development of a crowdfunding system, in Rails, in a 100\% remote and
      international team.

    \item{July 2012 - August 2013}
      {Ruby, Rails, Postgres}
      {Vivo}
      
      Development of a high availability control and monitoring system for cellphone
      network probes.

    \end{eventlist}

    \section{Education}

    \begin{yearlist}

    \item[B.Sc.]{2013 -- 2016}
      {Computer Science}
      {PUCRS}

    \item[B.Sc.]{2009 -- 2012}
      {Computer Engineering}
      {UFRGS}

    \end{yearlist}

    \section{Published Articles}
    \begin{yearlist}
    \item[Thesis]{2016}
      {Artificial Intelligence Methods Applied to Elevator Dispatching Using a Simulator}
      {Artificial Intelligence, Simulation}
    \end{yearlist}

    \section{Personal Projects}

    \begin{yearlist}

    \item{2018}
      {ate-chips \newline (\href{https://github.com/pedrovanzella/ate-chips}{github.com/pedrovanzella/ate-chips})}
      {Fully unit-tested Chip-8 emulator in C++}

    \item{2017}
      {do-the-webp \newline (\href{https://github.com/pedrovanzella/do-the-webp}{github.com/pedrovanzella/do-the-webp})}
      {Python package to convert DRM-Free comicbook files to webp}

    \item{2016}
      {intelevator \newline (\href{https://github.com/vantas/intelevator}{github.com/pedrovanzella/intelevator})}
      {Elevator simulator and planner in C++}
      
    \item{2015}
      {Flask-DODDNS \newline (\href{https://github.com/pedrovanzella/Flask-DODDNS}{github.com/pedrovanzella/Flask-DODDNS})}
      {Flask app that provides Dynamic DNS to home routers}

    \end{yearlist}

\end{document}
